---
title: "Formative Assessment 4"
author: "Dizon, Kiana Marie <br> Masicat, Lindsy Rossel "
date: "`r Sys.Date()`"
output: html_document
---


## Question Number 5

5. A geospatial analysis system has four sensors supplying images. The percentage of images supplied by each sensor and the percentage of images relevant
to a query are shown in the following table.

Sensor        | Percentage of Images Supplied   | Percentage of Relevant Images |TOTAL
------------- | --------------------------------| ------------------------------|-------
      1       |                 15              |                 50            |   65
      2       |                 20              |                 60            |   80
      3       |                 25              |                 80            |   105
      4       |                 40              |                 85            |   125
              |                                 |                               |
TOTAL         |                 100             |                 275           |   375
What is the overall percentage of relevant images?

Let E be the percentage of relevant images.

Let P(E) be the total probability of overall percentage of relevant images.

  P(E) = P(S1img ∩ E) + P(S2img ∩ E) + P(S3img ∩ E) + P(S4img ∩ E) <br>
  P(E) = P(S1img)P(E|S1img) + P(S2img)P(E|S2img) + P(S3img)P(E|S3img) + P(S4img)P(E|S4img) <br>
  P(E) = ((65/375) x (50/65)) + ((80/375) x (60/80)) + ((105/375) x (80/105)) + ((125/375) x (85/125))<br>
       
```{r 5}

  imgS1 <- 65
  imgS2 <- 80
  imgS3 <- 105
  imgS4 <- 125
  imgTotal <- 375
  ES1 <- 50
  ES2 <- 60
  ES3 <- 80
  ES4 <- 85
  
  ETotal <- ((imgS1/imgTotal)*(ES1/imgS1)) + ((imgS2/imgTotal)*(ES2/imgS2)) + ((imgS3/imgTotal)*(ES3/imgS3)) + ((imgS4/imgTotal)*(ES4/imgS4))

  ETotal

```

Therefore, the total probability of overall percentage of relevant images is 0.7333333 or 73%. 


## Question Number 6

6. A fair coin is tossed twice. 

Let E1 be the event that both tosses have the same outcome, that is, E1 = (HH, TT).

Let E2 be the event that the first toss is a head, that is, E2= (HH, HT). 

Let E3 be the event that the second toss is a head, that is, E3= (TH, HH). 

Show that E1, E2, and E3 are pairwise independent but not mutually independent. 

```{r number6}

sampleSpace <- c("HH", "HT", "TH", "TT")

E1 <- c("HH", "TT")
E2 <- c("HH", "HT")
E3 <- c("TH", "HH")

ProbE1 <- length(E1) / length(sampleSpace)
ProbE2 <- length(E2) / length(sampleSpace)
ProbE3 <- length(E3) / length(sampleSpace)

ProbE1andE2 <- length(intersect(E1, E2)) / length(sampleSpace)
ProbE1andE3 <- length(intersect(E1, E3)) / length(sampleSpace)
ProbE2andE3 <- length(intersect(E2, E3)) / length(sampleSpace)

pw_ind <- (ProbE1andE2 == ProbE1 * ProbE2) &
          (ProbE1andE3 == ProbE1 * ProbE3) &
          (ProbE2andE3 == ProbE2 * ProbE3)
pw_ind

cat("Since the value shows TRUE, therefore they are pairwise independent.")

ProbE1andE2andE3 <- length(intersect(intersect(E1, E2), E3)) / length(sampleSpace)
mutuallyInd <- ProbE1andE2andE3 == ProbE1 * ProbE2 * ProbE3

mutuallyInd
cat("Since the value shows FALSE, therefore they are not mutually independent.")
```
Thus, it shows that E1, E2, and E3 are pairwise independent but not mutually independent.
